О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-09 pps-linear-bound/pps-linear-lower-bound.tex
TODO note on using the term 'facher'
A theorem was cosmetically beautified

@@

\begin{theorem}
	For arbitrary integers $m \geq 2$, $n \geq m+1$, $d \geq 1$
	there is an integral point set $M$ of $n$ points in $m$-dimensional Euclidean space,
	so that for some $M_1, M_2\in M$ distance between $M_1$ and $M_2$ is exactly $d$.
\end{theorem}

>>>>

TODO: definition of facher IPS somewhere.

@@

\begin{theorem}
	For arbitrary integers $m \geq 2$, $n \geq m+1$, $d \geq 1$
	there exists $M\in\mathfrak{M}(m,n)$,
	such that for some $M_1, M_2\in M$ equality $|M_1 - M_2| = d$ holds.
\end{theorem}
